% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

Dear Hiring Manager,

\vspace{1em}

I am writing to express my strong interest in the System Analyst (Development) position. With over five years of experience in system engineering, cloud architecture, and software consulting---most recently as a Staff Consultant at Oracle Hong Kong---I have a proven track record of designing scalable enterprise solutions and modernizing legacy applications to drive tangible business value.

\vspace{1em}

In my current role at Oracle, I specialize in end-to-end software development, from requirements gathering through to deployment. Recently, I led the development of a Python and Java-based AI pipeline utilizing Llama 4 to automate expense invoice data extraction. This initiative achieved over 95\% accuracy and saved more than 30 minutes of manual processing time per user. I also spearheaded the modernization of a legacy 2003 Java system serving over 1,000 weekly public users. By systematically resolving critical security vulnerabilities and implementing automated, one-click Jenkins CI/CD pipelines, I significantly improved system stability and deployment efficiency. 

\vspace{1em}

My technical approach bridges robust backend engineering (Java, Spring Boot, Oracle DB) with modern frontend frameworks (Vue.js) and cloud-native practices (Docker, Kubernetes). Through developing enterprise-wide Oracle Integration Cloud (OIC) accounting applications for companies, I have honed my ability to translate complex business requirements into seamless, secure, and highly available technical workflows. Furthermore, my active certifications---including OCI Multicloud Architect and Kubernetes Engine Specialist---demonstrate my continuous commitment to staying at the forefront of cloud infrastructure and DevOps methodologies.

\vspace{1em}

I am particularly drawn to HKBU because of the positive experiences I have had collaborating with university staff in the past. The supportive, welcoming, and highly collaborative environment at HKBU stands out to me. I am eager to bring my expertise in full-stack development, AI integration, and enterprise cloud solutions to your team to help accelerate your upcoming technical initiatives.

\vspace{1em}

Thank you for considering my application. I have attached my resume for your review and would welcome the opportunity to discuss how my technical skills and consulting background align with your needs. 

\vspace{3em}

Sincerely,

\vspace{1em}

\textbf{Leo Hon}

\end{document}