% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Leo Hon}

\basicInfo{
  \email{leo.hon.work@gmail.com} \textperiodcentered\ 
  \phone{(+852) 97105733} \textperiodcentered\ 
  \linkedin[Leo Hon]{https://www.linkedin.com/in/leo-hon-4a1ba11aa/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Hong Kong Metropolitan University}, Hong Kong}{2018 -- 2020}
\textit{Bachelor of Computing with Honours} in Internet Technology
\datedsubsection{\textbf{Hong Kong Institute of Vocational Education}, Hong Kong}{2016 -- 2018}
\textit{Higher Diploma} in Software Engineering

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Oracle Hong Kong Ltd.} Hong Kong}{2021 -- Present}
\role{Staff Consultant}

\begin{itemize}
  \item \textbf{Financial \& ERP Systems}: Developed an Accounting Application based on Oracle Integration Cloud (OIC) for a 200+ employee company, processing 200+ monthly transactions. Designed approval workflows, file processing, and data integration between applications and Oracle DB.
  \item \textbf{AI Invoice Automation}: Engineered a Python/Java-based AI pipeline utilizing Llama 4 to extract data from expense documents with over 95\% accuracy, saving more than 30 minutes of manual processing time per user. Developed the frontend with Vue.js and backend with Spring Boot, incorporating Microsoft Azure AD for SSO and API integration.
  \item \textbf{System Upgrades \& CI/CD}: Created an automation tool to modernize a legacy 2003 Java system serving 50 internal and 1,000+ public weekly users, resolving 10+ high-severity security vulnerabilities. Implemented one-click Jenkins deployment pipelines and Git version control, and conducted post-upgrade load testing using JMeter.
  \item \textbf{Enterprise Support}: Managed requirements gathering, documentation, SIT/UAT, and production deployment for a JSP/Java EE banking system. Maintained and resolved bugs for existing mobile applications.
\end{itemize}

\datedsubsection{\textbf{Infocan,} Hong Kong}{2020 -- 2021}
\role{Full Time System Engineer}

\begin{itemize}
  \item \textbf{Student Attendance System}: Designed and implemented a student attendance system incorporating a QR code scanning feature, and maintained the underlying database systems.
  \item \textbf{E-commerce Platform}: Deployed a Magento shopping cart system utilizing Docker containerization. Developed custom interfaces and modules using PHP and JavaScript.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Main Programming Languages: Java, Python
  \item Frameworks: Spring Boot, VBCS, Struts
  \item Platform: Linux, Windows
  \item Database: MySQL, Oracle DB
  \item Tools: Docker, Jenkins, Git, OKE, JMeter, Llama 4
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{Become an OCI Foundations Associate (2022)}{2022}
\datedline{Oracle Cloud Infrastructure 2023 Multicloud Architect Certified Associate }{2024}
\datedline{Oracle Cloud Success Navigator Essentials}{2025}
\datedline{OCI Kubernetes Engine Specialist}{2025}
\datedline{Become an OCI AI Foundations Associate (2025)}{2025}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
